I would like to dedicate this work and take this opportunity to express my great appreciation and deep gratitude to the people and institutions who have helped and supported me along the way.
\\*

To my adviser, Dr. Eric A. Galapon, for his infinite patience, for his encouragement and guidance leading up to the accomplishment of this work. He's still the master of infinities.
\\*

To my thesis reader Dr. Francis Norman C. Paraan, and to my examiners Dr. Johnrob Y. Bantang and Dr. Marvin M. Flores, for the constructive criticism on how to improve this work. 
\\*

To the Office of the Chancellor of the University of the Philippines Diliman, through the Office of the Vice Chancellor for Research and Development, for funding this work through the Outright Research Grant Project No. 191915 ORG.
\\*

To the National Institute of Physics and University of the Philippines, for giving me a high-quality education and molding me into the person I am today. Lagi't lagi Para sa Bayan. 
\\*

To my colleagues at the Theoretical Physics Group, especially to the QuantMath subgroup for companionship and constant encouragement.
\\*

To my highschool and UP Manila and Diliman friends who still continue to support and encourage me even though we do not see each other more often. 
\\*

To my co-instructors, especially to Batch 2019 and socials people, for all the help and making everything bearable. 
\\*

To my badminton buddies, for the active and healthy activities in this pandemic.
\\*



To my physics batchmate, especially to my physics buddies JJ, Angelo, and Theo, for the support and push to finish this degree and this work.
\\*

To my solid team teach and classmate since UP Manila days, Ser Ralph Farrales, for helping me in both teaching and acads stuff.
\\*

To my favorite math prof, Dr. Mia Mojica, for the continuous support and believing in my skills.
\\*

To Leonarc Michelle Santos, for being my solid physics teammate since high school.
\\*

To Ma. Paula Rafaella M. Ortiz and to her family, for helping me in everything. Without them, I will not be here in UP Diliman.  
\\*

To Moira Isobel Christine Sapitula, for being a genuine and wonderful person.
\\*

To my futsal and ultimate friends, especially to Carl, Micah, Kenneth, Jonah, Gabriel, Adrianne, Cedie, Anel, Ivy, Louie, etc. for the chill online/in-person activities.
\\*

To my college bestfriend, Charlyn O. Valdeavilla, for always listening to me whatever it is. To her family, Daryl, Faye, Dong, Arlyn, for the trust, kindness, and always being there to help. 
\\*

And most especially to my parents and siblings as my unlimited source of motivation to continue and for their endless support. 


