\begin{thebibliography}{00}

@book{temme1996special,
  title={Special Functions: An Introduction to the Classical Functions of Mathematical Physics},
  author={Temme, N.M.},
  isbn={9780471113133},
  lccn={95042939},
  series={A Wiley-Interscience Publication},
  url={https://books.google.com.ph/books?id=7dQko2CndYoC},
  year={1996},
  publisher={Wiley}
}
https://www.overleaf.com/project/5c4a5a6d1192b10a8bb35797





% the original Stieltjes transform
\bibitem{widder} D. V. Widder, ``The Stieltjes transform'' Trans. Amer. Math. Soc. 43, 7-60 (1938).

% the generalized Stieltjes transform
\bibitem{saxena} R.K. Saxena, ``A study of the generalized Stieltjes transform'' 25, 340-355 (1959).

\bibitem{joshi} J.M.C. Joshi, ``On a generalized Stieltjes transform'' Pac. J. Math. 14, 969-975 (1964).

\bibitem{yurekli} O. Ycjrecli, ``A theorem on the generalized Stieltjes transform and its application'' J. Math. Anal. \& Appl. 168, 63-71 (1992).

\bibitem{schwarz} J.H. Schwarz, ``The generalized Stieltjes transform and its inverse'' J. Math. Phys. 46, 013501 (2005).

\bibitem{karp} D. Karp and E. Prilepkina, ``Generaluzed Stieltjes functions and their exact order'' J. Class. Anal. 1, 53-74 (2012).

% generalized Stieltjes transform extended to distributions
\bibitem{pathak} R.S. Pathak, L. Debnath, ``Recent developments on Stieltjes transform of generalized functions'', Internat. J. Math \& Math. Sci. 10, 641-670 (1987).

\bibitem{tekale} B. K. Tekale and M.S. Chaudary, ``On Stieltjes Transform of
Banach-Space-Valued Distributions'' J.Math. Anal. Appl. 139, 187-193 (1989).

\bibitem{hayek} N. Hayek, B.J. Gonzalez, E.R. Negrin, ``A variant of the Stieltjes transform on distributions of compact support'' Appl. Math. and Comp. 187, 2002-206 (2007).

%other generalizations of the Stieltjes transform
\bibitem{joshi2} J.C.M. Joshi, ``Recent studies in integral transforms'' J. Nat. \& Phys. Sci. 11, 65-78 (1997).

\bibitem{lopez} J.L. Lopez and C. Ferreira, ``Asymptotic Expansions of Generalized Stieltjes Transforms of Algebraically Decaying Functions'' Stud. Appl. Math. 108, 187-215 (2002).

\bibitem{hayek} N. Hayek, B.J. Gonzalez, E.R. Negrin, ``A variant of the Stieltjes transform on distributions of compact support,'' Appl. Math. and Comp. 187, 202-206 (2007) .

% applications of generalized Stieltjes transform in special functions
\bibitem{miana} P.J. Miana, ``Stieltjes transforms defined by $C_0$-semigroups,'' J. Comp. and Appl. Math. 234, 1172-1178 (2010).

\bibitem{ismail} M.E. Ismail, D.H. Kelkeri, ``Special functions, Stieltjes transforms and infinite divisibility,'' SIAM J. Math. Anal. 10, 884-901 (1979).

\bibitem{karp2} D. Karp and E. Prilepkina, ``Hypergeometric functions as generalized Stieltjes transforms'' J. Math. Anal. Appl. 393, 348???359 (2012).

%asymptotic expansion of the Stieltjes transform
\bibitem{wong} R. Wong {\it Asymptotic Approximations of Integrals}  SIAM (2001).

\bibitem{distribution} R. Wong, ``Distribution derivation of an asymptotic expansion,'' \textit{Proc. Amer. Math. Soc.} \textbf{80} (1980) 266.

\bibitem{mcwong} J.P. McClure, R. Wong, \lq\lq Explicit error terms for asymptotic expansions of Stieltjes transforms,\rq\rq \textit{J. Inst. Maths Applics} \textbf{3}(1)(1978) 129.

\bibitem{wong3} R. Wong, ``Explicit error terms for asymptotic expansions of Mellin convolutions,'' J. Math. Anal. Appl. 72, 740-756 (979).

\bibitem{kay} E.A. Galapon and K.M.L. Martinez, ``Exactification of the Poincaré asymptotic expansionof the Hankel integral: spectacularly accurate asymptotic expansions and non-asymptotic scales,'' {\it Proc. R. Soc. A} 470, 20130529 (2014).

\bibitem{lopez} J.L. Lopez, ``Asymptotic expansions of symmetric standard elliptic integrals,'' SIAM J. Math. Anal. 31, 754-775 (2000).

\bibitem{tica1}C. D. Tica and E. A. Galapon, “Finite-part integration of the generalized Stieltjes transform and its
dominant asymptotic behavior for small values of the parameter. I. Integer orders,” J. Math. Phys. 59(2),
023509 (2018).

\bibitem{tica2}C. D. Tica, E. A. Galapon. (2019) Finite-part integration of the generalized Stieltjes transform
and its dominant asymptotic behavior for small values of the parameter. II. Non-integer orders. Journal
of Mathematical Physics 60:1, 013502 (2019).

\bibitem{galapon2} E.A. Galapon, ``The problem of missing in term by term integration involving divergent integrals'' {\it Proc. R. Soc. A} 473, 20160567 (2017).

% finite part integral

\bibitem{hadamard} J. Hadamard, ``Lectures on Cauchy's problem in linear partial differential equations'' (1952).

\bibitem{fox} C. Fox {\it A generalization of the Cauchy principal value} Canad. J. Math. {\bf 9} 110-117 (1957).

\bibitem{monegato} G. Monegato, ``Definitions, properties and applications of finite-part integrals,'' Journal of Computational and Applied Mathematics 229, 425-439 (2009).

\bibitem{galapon1} E.A. Galapon, ``The Cauchy principal value and the Hadamard finite part integral as values of absolutely convergent integrals,''  {\it J. Math. Phys.} {\bf 57}, 033502 (2016).


%\bibitem{majda} Avellaneda and A.J. Majda, ``Stieltjes Integral Representation and Effective Diffusivity Bounds for Turbulent Transport'' Phys. Rev. Lett. 62, 753-755 (1989).

%\bibitem{majda2}. Avellaneda and A.J. Majda, ?``An integral representation and bounds on the effective diffusivity in passive advection by laminar and turbulent flows,'' Commun. Math. Phys. 138, 339-391 (1991).

%\bibitem{avellada} M. Avellaneda and M. Vergassola, ``Stieltjes integral representation of effective difFusivities in time-dependent flows'' Phys. Rev. E 52, 3249-3251 (1995).

%\bibitem{pavliotis} G.A. Pavliotis, ???Asymptotic analysis of the Green-Kubo formula, IMA J. Appl. Math. 75, 951-967 (2010).

%\bibitem{eidelman} S. Eidelman et. al., ???Testing non-perturbative strong interaction effects via the Adler function,??? Physics Letters B 454, 369???380 (1999).


\bibitem{simplepole2F2}
http://functions.wolfram.com/HypergeometricFunctions/Hypergeometric2F2/06/02/02/0003/

\bibitem{doublepole2F2}
http://functions.wolfram.com/HypergeometricFunctions/Hypergeometric2F2/06/02/03/0002/

\bibitem{2F1wolfram}
http://functions.wolfram.com/HypergeometricFunctions/Hypergeometric2F1/

\end{thebibliography}

